Analysis for Biracial Grade Retention Project

### 2022-09-02 analysis/analysis.Rmd
Add condensed summary table of resource differences by racial groups

```{r create-cf-marg}
coefs <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

coef_table_cf <- create_coef_table(coefs)
```

@@

>>>>

```{r create-cf-marg}
coefs_cf <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

coef_table_cf <- create_coef_table(coefs_cf)
```

@@

```{r tab-resources}
temp <- coefs_cf %>%
  select(term, estimate) %>%
  mutate(estimate=round(estimate,3)*100,
         term=as.character(term)) %>%
  rename(race=term, held_back_cf=estimate)

tbl_resources <- acs %>%
  group_by(race) %>%
  summarize(fam_inc=round(mean(family_income), 0),
            own_home=round(mean(own_home), 3)*100,
            m_ba=round(mean(degree_mother=="BA" | degree_mother=="G"), 3)*100,
            f_ba=round(mean(degree_father=="BA" | degree_father=="G"), 3)*100,
            f_born=round(mean(foreign_born), 3)*100,
            par_fb=round(mean(foreign_born_father | 
                                       foreign_born_mother), 3)*100,
            spk_eng_well=round(mean(spk_eng=="Yes"), 3)*100,
            spk_eng_par=round(mean(spk_eng_father=="Yes" & 
                                     spk_eng_mother=="Yes"), 3)*100) %>%
  mutate(race=as.character(race)) %>%
  left_join(temp) %>%
  arrange(held_back_cf)

index_biracial <- which(str_detect(tbl_resources$race, "/"))

tbl_resources %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Resource differences by race. Shading indicates biracial group.",
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race","mean family income","% own home",
                  "% mother, BA degree","% father, BA degree",
                  "% foreign-born","% either parent foreign-born",
                  "% speak English well", "% Both parents speak english well",
                  "% held back, counterfactual")) %>%
  kable_paper() %>%
  row_spec(index_biracial, background = "#D3D3D3")
```

The table sorts groups by their counterfactual probability of being held back. I think it does a nice job of summarizing the issues.
